EldersAIR initial home characteristics/activity data work

### 2020-06-09 home_adult_data_cleaning.Rmd
update file paths

# Load, format, and save home and adult overview/demographic data 
```{r}
# Load files 
## Box location: Update Box location once final data loaded
np_adult_initial <- read_xlsx("Input/NP/np_adult_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_id = as.factor(homeid),
         adult_id_char = as.factor(id),
         hispanic = as.factor(hispanic),
         race = as.factor(race),
         gender = as.factor(gender),
         consent_date = ymd(consentdate),
         area = "NP") %>% 
  select(adult_id_num, home_id, area, adult_id_char, hispanic, race, gender, consent_date) %>% 
  arrange(adult_id_num)

## Box location: Update Box location once final data loaded
nn_adult_initial <- read_xlsx("Input/NN/nn_adult_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_id = as.factor(homeid),
         adult_id_char = as.factor(id),
         hispanic = as.factor(hispanic),
         race = as.factor(race),
         gender = as.factor(gender),
         consent_date = ymd(consentdate),
         area = "NN") %>% 
  select(adult_id_num, home_id, area, adult_id_char, hispanic, race, gender, consent_date) %>% 
  arrange(adult_id_num)

@@

## Box location: Update Box location once final data loaded
np_homewinter_initial <- read_xlsx("Input/NP/np_homewinter_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  separate(interventiontime, c("trash1", "intervention_time"), sep = " ", remove = FALSE) %>%
  separate(samplingtime, c("trash1", "sampling_time_1"), sep = " ", remove = FALSE) %>%
  separate(pickuptime, c("trash1", "pickup_time_1"), sep = " ", remove = FALSE) %>%
  separate(sampling2time, c("trash1", "sampling_time_2"), sep = " ", remove = FALSE) %>%
  separate(pickup2time, c("trash1", "pickup_time_2"), sep = " ", remove = FALSE) %>%
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(intervention_time),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(sampling_time_1),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickup_time_1),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling_time_2),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup_time_2),
         area = "NP") %>% 
  select(home_id, winter_id, home_winter_id, area, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2) %>% 
  filter(!is.na(home_id)) %>% 
  arrange(home_id, winter_id)

## Box location: Update Box location once final data loaded
nn_homewinter_initial <- read_xlsx("Input/NN/nn_homewinter_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  separate(interventiontime, c("trash1", "intervention_time"), sep = " ", remove = FALSE) %>%
  separate(samplingtime, c("trash1", "sampling_time_1"), sep = " ", remove = FALSE) %>%
  separate(pickuptime, c("trash1", "pickup_time_1"), sep = " ", remove = FALSE) %>%
  separate(sampling2time, c("trash1", "sampling_time_2"), sep = " ", remove = FALSE) %>%
  separate(pickup2time, c("trash1", "pickup_time_2"), sep = " ", remove = FALSE) %>%
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(intervention_time),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(sampling_time_1),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickup_time_1),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling_time_2),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup_time_2),
         area = "NN") %>% 
  select(home_id, winter_id, home_winter_id, area, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2) %>% 
  filter(!is.na(home_id)) %>% 
  arrange(home_id, winter_id)

@@

## Box location: Update Box location once final data loaded
np_home_initial <- read_xlsx("Input/NP/np_home_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition),
         area = "NP") %>% 
  select(home_id, home, treatment, area)

## Box location: Update Box location once final data loaded
nn_home_initial <- read_xlsx("Input/NN/nn_home_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition),
         area = "NN") %>% 
  select(home_id, home, treatment, area)

@@

# Combine adult, home, homewinter files
```{r}
elders_ids_linked <- elders_homewinter %>% 
  left_join(elders_home, by = c("area", "home_id")) %>% 
  left_join(elders_adult, by = c("area", "home_id")) %>% 
  mutate(home = str_remove(home, "[_]"))
#write_rds(elders_ids_linked, "Output/elders_ids_linked.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load, format, and save home and adult overview/demographic data 
```{r}
# Load files 
## Box location: Update Box location once final data loaded
np_adult_initial <- read_xlsx(paste0(file_path, "Input/NP/np_adult_20200220.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_id = as.factor(homeid),
         adult_id_char = as.factor(id),
         consent_date = ymd(consentdate),
         area = "NP") %>% 
  select(adult_id_num, home_id, area, adult_id_char, consent_date) %>% 
  arrange(adult_id_num)

## Box location: Update Box location once final data loaded
nn_adult_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_adult_20200220.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_id = as.factor(homeid),
         adult_id_char = as.factor(id),
         consent_date = ymd(consentdate),
         area = "NN") %>% 
  select(adult_id_num, home_id, area, adult_id_char, consent_date) %>% 
  arrange(adult_id_num)

@@

# Load files 
## Box location: Update Box location once final data loaded
np_demographics_initial <- read_xlsx(paste0(file_path, "Input/NP/np_demographics_20200225.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_winter_id = as.factor(homewinterid),
         gender = factor(gender),
         hispanic = factor(hispanic),
         race = factor(race),
         income = factor(income),
         education = factor(education),
         total_residents = as.numeric(totalres),
         residents_under18 = as.numeric(undereighteen),
         age_nov1 = as.numeric(agenov1),
         area = "NP") %>% 
  select(adult_id_num, home_winter_id, area, gender, hispanic, race, income, 
         education, total_residents, residents_under18, age_nov1) %>% 
  arrange(adult_id_num)

## Box location: Update Box location once final data loaded
nn_demographics_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_demographics_20200225.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_winter_id = as.factor(homewinterid),
         gender = factor(gender),
         hispanic = factor(hispanic),
         race = factor(race),
         income = factor(income),
         education = factor(education),
         total_residents = as.numeric(totalres),
         residents_under18 = as.numeric(undereighteen),
         age_nov1 = as.numeric(agenov1),
         area = "NN") %>% 
  select(adult_id_num, home_winter_id, area, gender, hispanic, race, income, 
         education, total_residents, residents_under18, age_nov1) %>% 
  arrange(adult_id_num)

elders_demographics <- rbind(np_demographics_initial, nn_demographics_initial)

## Box location: Update Box location once final data loaded
np_homewinter_initial <- read_xlsx(paste0(file_path, "Input/NP/np_homewinter_20200220.xlsx")) %>% 
  rename_all(tolower) %>% 
  separate(interventiontime, c("trash1", "intervention_time"), sep = " ", remove = FALSE) %>%
  separate(samplingtime, c("trash1", "sampling_time_1"), sep = " ", remove = FALSE) %>%
  separate(pickuptime, c("trash1", "pickup_time_1"), sep = " ", remove = FALSE) %>%
  separate(sampling2time, c("trash1", "sampling_time_2"), sep = " ", remove = FALSE) %>%
  separate(pickup2time, c("trash1", "pickup_time_2"), sep = " ", remove = FALSE) %>%
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(intervention_time),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(sampling_time_1),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickup_time_1),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling_time_2),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup_time_2),
         area = "NP") %>% 
  select(home_id, winter_id, home_winter_id, area, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2) %>% 
  filter(!is.na(home_id)) %>% 
  arrange(home_id, winter_id)

## Box location: Update Box location once final data loaded
nn_homewinter_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_homewinter_20200220.xlsx")) %>% 
  rename_all(tolower) %>% 
  separate(interventiontime, c("trash1", "intervention_time"), sep = " ", remove = FALSE) %>%
  separate(samplingtime, c("trash1", "sampling_time_1"), sep = " ", remove = FALSE) %>%
  separate(pickuptime, c("trash1", "pickup_time_1"), sep = " ", remove = FALSE) %>%
  separate(sampling2time, c("trash1", "sampling_time_2"), sep = " ", remove = FALSE) %>%
  separate(pickup2time, c("trash1", "pickup_time_2"), sep = " ", remove = FALSE) %>%
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(intervention_time),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(sampling_time_1),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickup_time_1),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling_time_2),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup_time_2),
         area = "NN") %>% 
  select(home_id, winter_id, home_winter_id, area, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2) %>% 
  filter(!is.na(home_id)) %>% 
  arrange(home_id, winter_id)

@@

## Box location: Update Box location once final data loaded
np_home_initial <- read_xlsx(paste0(file_path, "Input/NP/np_home_20200220.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition),
         area = "NP") %>% 
  select(home_id, home, treatment, area)

## Box location: Update Box location once final data loaded
nn_home_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_home_20200220.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition),
         area = "NN") %>% 
  select(home_id, home, treatment, area)

@@

# Combine adult, home, homewinter files
```{r}
elders_ids_linked <- elders_homewinter %>%
  filter(winter_id != 3) %>% 
  left_join(elders_demographics, by = c("area", "home_winter_id")) %>% 
  left_join(elders_home, by = c("area", "home_id")) %>% 
  left_join(elders_adult, by = c("area", "home_id", "adult_id_num")) %>% 
  mutate(home = str_remove(home, "[_]")) %>% 
  arrange(area, home, winter_id)
#write_rds(elders_ids_linked, paste0(file_path, "Output/elders_ids_linked.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))
```

### 2020-06-09 home_char_act_summary.Rmd
update file paths

```{r}
# Load dataset
home_char_clean <- read_rds("Output/elders_home_char_clean.rds")
home_act_clean <- read_rds("Output/elders_home_activity_clean.rds")
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
elders_pm <- read_rds("Output/elders_pm_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

# Load dataset
home_char_clean <- read_rds(paste0(file_path, "Output/elders_home_char_clean.rds"))
home_act_clean <- read_rds(paste0(file_path, "Output/elders_home_activity_clean.rds"))
elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds"))
```

### 2020-06-09 home_characteristics_activity_cleaning.Rmd
update file paths

# Load, format, and save home characteristics data
```{r}
## Box location: Update Box location once final data loaded
np_homechar_initial <- read_xlsx("Input/NP/np_homechar_20200225.xlsx") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.numeric(Residents),
         residents_over55 = as.numeric(Over55),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.numeric(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.numeric(NumFloors),
         home_bedrooms = as.numeric(NumBedrooms),
         home_windows = as.numeric(NumWindows),
         home_pets = as.numeric(NumPets),
         home_furry = as.numeric(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         wood_collect = as.factor(WhenGet),
         wood_collect_method = as.factor(AcquireFrom),
         wood_cords = as.numeric(Cords),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "NP") %>% 
  select(home_winter_id, area, residents_total, residents_over55,
         residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, wood_collect,
         wood_collect_method, wood_cords, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

## Box location: Update Box location once final data loaded
nn_homechar_initial <- read_xlsx("Input/NN/nn_homechar_20200225.xlsx") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.numeric(Residents),
         residents_over55 = as.numeric(Over55),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.numeric(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.numeric(NumFloors),
         home_bedrooms = as.numeric(NumBedrooms),
         home_windows = as.numeric(NumWindows),
         home_pets = as.numeric(NumPets),
         home_furry = as.numeric(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         wood_collect = as.factor(WhenGet),
         wood_collect_method = as.factor(AcquireFrom),
         wood_cords = as.numeric(Cords),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "NN") %>% 
  select(home_winter_id, area, residents_total, residents_over55,
         residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, wood_collect,
         wood_collect_method, wood_cords, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

#write_rds(elders_home_char, "Output/elders_home_char.rds")
```

# Clean up all home characteristics data
```{r}
elders_home_char <- read_rds("Output/elders_home_char.rds")

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")

@@

# write_rds(elders_home_char_clean, "Output/elders_home_char_clean.rds")

elders_home_char_clean <- read_rds("Output/elders_home_char_clean.rds")
```

@@

# Load, format, and save home activity data
```{r}
## Box location: Update Box location once final data loaded
np_homeactivity_initial <- read_xlsx("Input/NP/np_homeactivity_20200225.xlsx") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         home_act_day = as.factor(Day),
         home_act_gas = as.factor(Gas),
         home_act_elect = as.factor(Electrical),
         home_act_propane = as.factor(Propane),
         home_act_oil = as.factor(Oil),
         home_act_other = as.factor(Other),
         home_act_smoking = as.factor(Smoking),
         home_act_incense = as.factor(Incense),
         home_act_candle = as.factor(Candle),
         home_act_kerosene = as.factor(Kerosene),
         home_act_windows = as.factor(OpenWindows),
         home_act_door = as.factor(OpenDoor),
         home_act_sweep = as.factor(Sweeping),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  select(home_winter_id, area, sampling_visit, home_act_day,
         home_act_gas, home_act_elect, home_act_propane,
         home_act_oil, home_act_other, home_act_smoking,
         home_act_incense, home_act_candle, home_act_kerosene,
         home_act_windows, home_act_door, home_act_sweep) %>% 
  ungroup() %>% 
  arrange(home_winter_id, home_act_day)

## Box location: Update Box location once final data loaded
nn_homeactivity_initial <- read_xlsx("Input/NN/nn_homeactivity_20200225.xlsx") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         home_act_day = as.factor(Day),
         home_act_gas = as.factor(Gas),
         home_act_elect = as.factor(Electrical),
         home_act_propane = as.factor(Propane),
         home_act_oil = as.factor(Oil),
         home_act_other = as.factor(Other),
         home_act_smoking = as.factor(Smoking),
         home_act_incense = as.factor(Incense),
         home_act_candle = as.factor(Candle),
         home_act_kerosene = as.factor(Kerosene),
         home_act_windows = as.factor(OpenWindows),
         home_act_door = as.factor(OpenDoor),
         home_act_sweep = as.factor(Sweeping),
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  select(home_winter_id, area, sampling_visit, home_act_day,
         home_act_gas, home_act_elect, home_act_propane,
         home_act_oil, home_act_other, home_act_smoking,
         home_act_incense, home_act_candle, home_act_kerosene,
         home_act_windows, home_act_door, home_act_sweep) %>% 
  ungroup() %>% 
  arrange(home_winter_id, home_act_day)

@@

#write_rds(elders_home_activity, "Output/elders_home_activity.rds")
```

# Clean up all home activity data
```{r}
elders_home_activity <- read_rds("Output/elders_home_activity.rds")

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")

@@

# write_rds(elders_home_activity_clean, "Output/elders_home_activity_clean.rds")

elders_home_activity_clean <- read_rds("Output/elders_home_activity_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load, format, and save home characteristics data
```{r}
## Box location: Update Box location once final data loaded
np_homechar_initial <- read_xlsx(paste0(file_path, "Input/NP/np_homechar_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.numeric(Residents),
         residents_over55 = as.numeric(Over55),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.numeric(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.numeric(NumFloors),
         home_bedrooms = as.numeric(NumBedrooms),
         home_windows = as.numeric(NumWindows),
         home_pets = as.numeric(NumPets),
         home_furry = as.numeric(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         wood_collect = as.factor(WhenGet),
         wood_collect_method = as.factor(AcquireFrom),
         wood_cords = as.numeric(Cords),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "NP") %>% 
  select(home_winter_id, area, residents_total, residents_over55,
         residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, wood_collect,
         wood_collect_method, wood_cords, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

## Box location: Update Box location once final data loaded
nn_homechar_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_homechar_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         residents_total = as.numeric(Residents),
         residents_over55 = as.numeric(Over55),
         residents_smoke = as.factor(Smoke),
         residents_smoke_inside = as.factor(SmokeInside),
         home_type = as.factor(HomeType),
         home_year_built = as.numeric(YearHomeBuilt),
         home_sqft = as.numeric(SqFootage),
         home_floors = as.numeric(NumFloors),
         home_bedrooms = as.numeric(NumBedrooms),
         home_windows = as.numeric(NumWindows),
         home_pets = as.numeric(NumPets),
         home_furry = as.numeric(NumFurryPets),
         primary_heat = as.factor(PrimaryHeat),
         secondary_heat = as.factor(SecondaryHeat),
         stove_model = as.character(WoodstoveModel),
         stove_age = as.factor(WoodstoveAge),
         stove_cert = as.factor(WoodstoveEPACert),
         wood_collect = as.factor(WhenGet),
         wood_collect_method = as.factor(AcquireFrom),
         wood_cords = as.numeric(Cords),
         chimney_clean = as.factor(ChimneyCleaned),
         home_damp = as.factor(Damp),
         home_mold = as.factor(Mold),
         home_fireplace = as.factor(ExistingFireplace),
         home_furnace = as.factor(ExistingFurnace),
         home_woodstove = as.factor(ExistingWoodstove),
         home_insert = as.factor(ExistingInsert),
         area = "NN") %>% 
  select(home_winter_id, area, residents_total, residents_over55,
         residents_smoke, residents_smoke_inside,
         home_type, home_year_built, home_sqft, home_floors, home_bedrooms,
         home_windows, home_pets, home_furry, primary_heat,
         secondary_heat, stove_model, stove_age, stove_cert, wood_collect,
         wood_collect_method, wood_cords, chimney_clean,
         home_damp, home_mold, home_fireplace, home_furnace,
         home_woodstove, home_insert) %>% 
  ungroup() %>% 
  arrange(home_winter_id)

@@

#write_rds(elders_home_char, paste0(file_path, "Output/elders_home_char.rds"))
```

# Clean up all home characteristics data
```{r}
elders_home_char <- read_rds(paste0(file_path, "Output/elders_home_char.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

@@

# write_rds(elders_home_char_clean, paste0(file_path, "Output/elders_home_char_clean.rds"))

elders_home_char_clean <- read_rds(paste0(file_path, "Output/elders_home_char_clean.rds"))
```

@@

# Load, format, and save home activity data
```{r}
## Box location: Update Box location once final data loaded
np_homeactivity_initial <- read_xlsx(paste0(file_path, "Input/NP/np_homeactivity_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         home_act_day = as.factor(Day),
         home_act_gas = as.factor(Gas),
         home_act_elect = as.factor(Electrical),
         home_act_propane = as.factor(Propane),
         home_act_oil = as.factor(Oil),
         home_act_other = as.factor(Other),
         home_act_smoking = as.factor(Smoking),
         home_act_incense = as.factor(Incense),
         home_act_candle = as.factor(Candle),
         home_act_kerosene = as.factor(Kerosene),
         home_act_windows = as.factor(OpenWindows),
         home_act_door = as.factor(OpenDoor),
         home_act_sweep = as.factor(Sweeping),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  select(home_winter_id, area, sampling_visit, home_act_day,
         home_act_gas, home_act_elect, home_act_propane,
         home_act_oil, home_act_other, home_act_smoking,
         home_act_incense, home_act_candle, home_act_kerosene,
         home_act_windows, home_act_door, home_act_sweep) %>% 
  ungroup() %>% 
  arrange(home_winter_id, home_act_day)

## Box location: Update Box location once final data loaded
nn_homeactivity_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_homeactivity_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         home_act_day = as.factor(Day),
         home_act_gas = as.factor(Gas),
         home_act_elect = as.factor(Electrical),
         home_act_propane = as.factor(Propane),
         home_act_oil = as.factor(Oil),
         home_act_other = as.factor(Other),
         home_act_smoking = as.factor(Smoking),
         home_act_incense = as.factor(Incense),
         home_act_candle = as.factor(Candle),
         home_act_kerosene = as.factor(Kerosene),
         home_act_windows = as.factor(OpenWindows),
         home_act_door = as.factor(OpenDoor),
         home_act_sweep = as.factor(Sweeping),
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  select(home_winter_id, area, sampling_visit, home_act_day,
         home_act_gas, home_act_elect, home_act_propane,
         home_act_oil, home_act_other, home_act_smoking,
         home_act_incense, home_act_candle, home_act_kerosene,
         home_act_windows, home_act_door, home_act_sweep) %>% 
  ungroup() %>% 
  arrange(home_winter_id, home_act_day)

@@

#write_rds(elders_home_activity, paste0(file_path, "Output/elders_home_activity.rds"))
```

# Clean up all home activity data
```{r}
elders_home_activity <- read_rds(paste0(file_path, "Output/elders_home_activity.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

@@

# write_rds(elders_home_activity_clean, paste0(file_path, "Output/elders_home_activity_clean.rds"))

elders_home_activity_clean <- read_rds(paste0(file_path, "Output/elders_home_activity_clean.rds"))
```
